Analyses of Promises in R

### 2018-04-19 old-analysis/report-interactions-among-promises.Rmd

# Drawing
grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))

>>>>

# Drawing
g <- grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
g
save_graph("interactions-among-promises.pdf", g)
save_graph("promise-interactions-receive.pdf", g_receive)
save_graph("promise-interactions-cause-small.pdf", g_cause_small)
save_graph("promise-interactions-cause-big.pdf", g_cause_big)

### 2018-04-19 old-analysis/report-main.Rmd

pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
load_local_csv <- function (csv_file, backup=NULL) {
    path <- file.path(params$CSV_DIR, csv_file)
    write(paste("reading", path), stderr())
    tryCatch( 
      as_tibble(read.csv(path, stringsAsFactors=FALSE)),
      error=function(e) backup
    )
}
print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
prettify <- function(x) x %>% mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>% as.data.frame
pp_trunc <- function(x) ifelse(x==0, paste(format(x, digits=2, scientific=FALSE)),
                               ifelse(x < 1000, format(x, digits=2, scientific=FALSE), 
                                      ifelse(x < 1000000, 
                                             paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""),
                                             ifelse(x < 1000000000,
                                                    paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""),
                                                    paste(format(floor((x/1000000000)*10)/10, digits=2, scientific=FALSE), "b", sep="")))))
pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
is_outlier <- function(x) x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x)

>>>>

pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
load_local_csv <- function (csv_file, backup=NULL) {
    path <- file.path(params$CSV_DIR, csv_file)
    write(paste("reading", path), stderr())
    tryCatch( 
      as_tibble(read.csv(path, stringsAsFactors=FALSE)),
      error=function(e) backup
    )
}
save_graph <- function(pdf_file, graph) {
    path <- file.path(params$CSV_DIR, pdf_file)
    write(paste("writing graph to", path), stderr())
    ggsave(path, graph, device="pdf")
}
print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
prettify <- function(x) x %>% mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>% as.data.frame
pp_trunc <- function(x) ifelse(x==0, paste(format(x, digits=2, scientific=FALSE)),
                               ifelse(x < 1000, format(x, digits=2, scientific=FALSE), 
                                      ifelse(x < 1000000, 
                                             paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""),
                                             ifelse(x < 1000000000,
                                                    paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""),
                                                    paste(format(floor((x/1000000000)*10)/10, digits=2, scientific=FALSE), "b", sep="")))))
pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
is_outlier <- function(x) x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x)

### 2018-04-19 old-analysis/report-number-of-accesses-to-a-promise.Rmd

ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
  theme(axis.title.x=element_blank(), legend.position="none") +
	ylab("No. of promises") + xlab("No. of accesses")

>>>>

g <- ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
  theme(axis.title.x=element_blank(), legend.position="none") +
	ylab("No. of promises") + xlab("No. of accesses")
g
save_graph("promise-evaluations.pdf", g)

### 2018-04-19 report/05-position-evaluation-mode.Rmd

```{r echo=FALSE, message=FALSE}
show_graph("position-evaluation-mode", "evaluation_mode_distribution.png")
```

>>>>

```{r echo=FALSE, message=FALSE}
show_graph("position-evaluation-mode", "evaluation_mode_distribution_by_function.png")
```

```{r echo=FALSE, message=FALSE}
show_graph("position-evaluation-mode", "evaluation_mode_distribution_by_formal_parameter_position.png")
```

### 2018-04-19 report/analysis.Rmd

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(methods) ## including this prevents a warning - "executing load actions ..."
library(DT)
library(tidyverse)
library(knitr)
library(png)
library(grid)
library(gridExtra)
library(broom)
library(tidyr)
```

@@

show_table <- function(analysis_name, table_filename) {
    get_table(analysis_name, table_filename) %>%
    datatable(rownames = FALSE, options = list(scrollX = TRUE))
}
```

>>>>

---
title: "Analyses of Promises in R"
author: "Aviral Goel"
output: 
  html_document:
    theme: flatly
    highlight: tango
    keep_md: true
    toc: true
    toc_float: true
    number_sections: true
params:
  analysis_output_dir: TRUE
---

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(methods) ## including this prevents a warning - "executing load actions ..."
library(DT)
library(tidyverse)
library(knitr)
library(png)
library(grid)
library(gridExtra)
```

@@

show_table <- function(analysis_name, table_filename) {
    get_table(analysis_name, table_filename) %>%
    datatable(rownames = FALSE)
}
```
